\documentclass[11pt,notitlepage]{article}

\usepackage{titlesec}
\usepackage[margin=1in]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

%\titlespacing*{\section}{0pt}{0pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing*{\subsection}{0pt}{0pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing*{\subsubsection}{0pt}{0pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\begin{document}
\section*{Budget Justification}

\subsection{Personnel}

\subsubsection{Stephen Ramsey, Oregon State U., 2.0 months effort}
Dr.~Ramsey will be responsible for (i) overall project management and
coordination and (ii) communication with NCATS and Translator stakeholders. He
will contribute to the work of knowledge graph-traversal component of the
Reasoning Tool (see Sec.~\ref{sec:koslicki}). 

\subsubsection{David Koslicki, Oregon State U., 2.0 months effort}
\label{sec:koslicki}
Dr.~Koslicki will be responsible for implementing the knowledge graph-traversal
component of the Reasoning Tool. 

\subsubsection{Liang Huang, Oregon State U., 2.0 months effort}
Dr.~Huang will be responsible for the natural-language processing capabilities of
the Reasoning Tool. He will contribute two months of effort to the
project.

\subsubsection{Arnab Nandi, Ohio State U., 2.0 months effort}
Dr.~Nandi will be responsible for the Human-in-the-Loop Data Exploration System (HILDES)
portion of the Reasoning Tool. 

\subsubsection{Theo Knijnenburg, ISB, 2.0 months effort}
Dr.~Knijnenburg will be jointly responsible (with Dr.~Deutsch) for software
interface of the Reasoning Tool with the Translator system (including Blackboard
and Knowledge Sources). He will also be responsible for developing software
workflows for statistical analysis of large-scale knowledge graphs. 

\subsubsection{Eric Deutsch, ISB, 2.0 months effort}
Dr.~Deutsch will be jointly responsible (with Dr.~Knijnenburg) for software
interface of the Reasoning Tool with the Translator system (including Blackboard
and Knowledge Sources). He will also be responsible for developing software
workflows for statistical analysis of large-scale knowledge graphs.

\section{Travel}

\section{Cloud Computing}


\end{document}
